Title

### 2018-05-15 paperdraft.Rmd
up

---
title: "How Does The Scope of Framing Affect Stakeholders' Evaluation of Firms?"
subtitle: "Evidence from China's State-Owned Enterprises"
author: 'Ying Li'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
geometry: margin=1.5in
fontsize: 12pt
bibliography: ref.bib
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = F,
                      tidy=T, 
                      tidy.opts=list(width.cutoff=60),
                      results='hide',
                      strip.white=TRUE,
                      fig.path='figs/fig',
                      cache=F,
                      highlight=TRUE,
                      out.width='.9\\textwidth',
                      out.extra="",
                      message=FALSE,
                      warning=FALSE,
                      error=FALSE,
                      comment=NA,
                      size='footnotesize',
                      options(digits=3,xtable.comment=FALSE))
```

@@

# Overview
Evaluation is one of the most basic social processes [@lamont12]. In the business world, garnering positive evaluations from key stakeholders such as government, media, business partners and so on is crucial for organizations to gain legitimacy, obtain resources and establish competitive advantages [@bite11]. Since social evaluation involves an information-processing mechanism that is often subjected to human cogitive and emotional factors, stakeholders' evaluation can heavily be influenced by how firms present themselves. A successful framing strategy, therefore, is essential for firms to project their identities, deliever important information, and guide social evaluation.

@@

##Variables and Measurement
```{r cleaning2}
# Manually check for overly influential points
library(xtable)
tabarea <- t(table(mydata$area1))
print(xtable(tabarea,label="tab:area",caption="Frequency of Areas. Only four observations in the overseas group is a warning signal for micronumeriosity."),caption.placement = "top")
print(xtable(prop.table(table(mydata$award,mydata$area1),margin=2),
             label="tab:areaaward",
             caption = "Overly Influential Points from the Overseas Area"),
      caption.placement = "top")
n_overseas <- nrow(mydata[mydata$area1=="Overseas",])
newn <- n-n_overseas
# delete four overseas firms
mydata<-mydata[!(mydata$area1=="Overseas"),]
```

@@

*Framing Focus* is the independent variable in this paper. It measures how balanced an application file is across different innovation topics. I measure this variable by calculating the standard deviation of the coverage probabilities in the three largest innovation topics in an application report. Higher Framing Focus represents that a firm is more focused on one topic instead of spanning multiple topics at the same time. The larger the value of Framing Focus, the narrower the firm frames its innovation accompolishment. For example, if the three largest coverage probabilities for firm A is (0.3, 0.3, 0.3) and for firm B is (0.4, 0.3, 0.2), then the Framing Focus for A and B are 0 and 0.1, meaning that A tries to span across multiple topics while B tries to be more focused on a smaller number of topics.

I only choose the three largest innovation topics because three different categories is already an upper limit of information for evaluators to notice and process. If all the 27 innovation topics are used, it only adds more noise because in reality almost no applicant is able to innovate in so many areas, nor would they aim to cover all the innovation topics simultaneously. For a robustness check, I also measured framing focus across four innovation topics and results are similar. In terms of the appropiateness of measurement, according to Figure 1 in @adco11, this measurement could satisfy both a top-down and bottom-up justification on four levels of conceptualization. In this paper, the background concept is firm self-presentation; the systematized concept is framing; the indicator is the focusing/spanning framing strategy of presenting innovation accomplishments in the application reports; scores for cases are standard deviations of the three most salient innovation topics' coverage.

### Control Variables
I added five control variables. *Area*. All the SOEs are divided and into four areas: North, South, East, and West. The regional economic development is very uneven in China. SOEs from different areas often could have different framing strategies to present themselves and the government also evaluate SOEs from differently areas by different criteria. *Scale*. Whether an applicant firm is large- or small-size affects its ability to innovate, to frame its innovation accomplishments and thus affect its winning probability. *Ownership*. Whether an applicant firm is a Central SOE, Ordinary SOE, or other forms directly affects how much resources it can get from the central government. Ownership type is an important marker of SOE differences. *Industry*. Different industries are subjected to different evaluation criteria and tendencies to frame their innovation. I measure the industry variable by referring to the industry topic that has the largest coverage proportion. *Industry Scope*. Industry Scope is actually a second form of framing --- framing the industrial identities. Chinese SOEs are often big bureaucracies that operate across multiple industries. Some of them are so diversfied because of historical reasons of assuming a specifice social responsibility. Government may treat firms differently if they express their multi-industry identities in the application reports, and if a firm has a broader scope of framing in industry, it is more likely to have a broader scope of framing in innovation. I measure this variable by calculating the standard deviation of topic coverage proportions across the three largest covered industry topics.

@@

## Statistical Inference
I'm interested in infering the partial relationship between Framing Focus and probability of winning an award. I'm not using an experiment or a quasi-experiment (e.g. using matching to create an "as if" experiment) design, because my major variable of interest is continuous and dichotomizing it would sacrifice valuable information. Instead, I use a model-based design. For a OlS model, the data generating process gives probabilities of winning an award through a normal distribution. For a logit model, the data generating process gives a wining or losing binary outcome which conforms to a Bernoulli distribution. For both models, the probability of having a "success" outcome depends on a set of variables, which are ones that are listed as control variables plus the Framing Focus variable.

@@

### OLS
```{r ols}
# ols model
ols.model <- lm(award~ area + ownership + scale + industry + indvar + innvar, data = newdata)
summary(ols.model)
pred.ols <- predict(ols.model)
range <- range(pred.ols)
# bootstrapping
library(dplyr)
set.seed(1111)
bootstrap <-data.frame(t(replicate(1000,coef(lm(award~ area + ownership + scale + industry + indvar + innvar,data=sample_n(newdata,size=nrow(newdata),replace=TRUE))))))
coveint <- quantile(bootstrap[,"innvar"],c(.025,.975))
est <- mean(bootstrap[,"innvar"]) # Estimates from bootstrapping
est.sub <- sprintf("%.1f%%", est * 10) # for interpretation use
est0 <- summary(ols.model)$coef['innvar',1] # Estimates from the canned OLS model
car::vif(ols.model)
```
A binary outcome variable is not an adequate reason to exclude using OLS, especially considering that the predicted y range can provide us extra information to evaluate model specification and that we can have multiple techniques to correct for heterogeneity problems. Therefore, I first tried OLS to estimate the relationship between Framing Focus and winning proabilities.

@@

### Logistic Regression
The model specification for logistic regression is as follows:
\begin{equation}
\begin{split}
log \frac{Pr(award)}{1-Pr(award)}= \beta_{0}+\beta_{1}framing + \beta_{2}area + \beta_{3}ownership \\
+\beta_{4}scale +\beta_{5}industry + \beta_{6}industry scope + \epsilon
\end{split}
\end{equation}
Generally, for maximum likelihood method for estimation and inference, the estimates come from first-order derivative of the log likelihood function-- when the first-order derivative equals 0 the likelihood of observing the data is maximized (or minimized depending on the sign of the second derivative at this turning point), and the standard errors come from the second-order derivative. When I use logistic regression, I use maximum likelihood principles to derive estimates and standard errors. The p-values come from comparing against a t-distribution with the estimate being the mean and the stand errors being the standard deviance, what's the chance of observing such an estimate given the model is true. In other words, I'm relying on CLT here to make a reference, which is plausible given the large observation numbers of this study.

@@

# comparison of multiple link functions
pdf("pplot.pdf")
par(mfrow=c(1,2))  
plot(pred.logit,pred.probit)
plot(pred.logit,pred.clog)
dev.off()
c(logLik(logit.model),logLik(probit.model),logLik(clog.model))
```
```{r presentation, results='asis'}
est.logit <- logit.model$coefficients["innvar"]
exp.logit <- exp(0.1*est.logit)
stargazer(logit.model,omit="industry",omit.labels = "Industry Dummies", header=F,
          font.size = "small",
          title ="Maximum Likelihood Estimates for Award-Winning Odds Ratio",
          covariate.labels = c("North Area","South Area","West Area","Ordinary SOEs","Other SOEs","Small SOEs","Industry Scope","Framing Focus"),
          dep.var.labels = "Award-Winning Odds Ratio",
          label="tab:logit" #, type='text'
          )
```
Table \ref{tab:logit} describes the results of the logistic regression. The advantage of a logit model is that predictions of the dependent variable can be strictly bounded between 0 and 1. The disadvantage is that overfitting is a frequent encountered problem, but after dealing with the overly influencial points, there are no apparent evidence of overfitting. 
\begin{figure}
\includegraphics[width=0.6\textwidth]{pplot.pdf}
\caption{Comparison of the Predicted Probabilities of Logit, Probit and cloglog Links}
\label{fig:pplot}
\end{figure}

Admittedly, logit is not the only link function that can transform $X\beta$, so I also tried probit and cloglog link functions. The log likelihoods across these three link models are very close to each other and the PP-plots (Figure \ref{fig:pplot}) show that the predicted probablities are around a 45 degree line. Given the relative advantage of interpretation of odds ratio, I only present the results of a logit model here^[I would love to evaluate the link functions using the method of [@roger06], but I have to admit that given my R skills and the limited time, manually comparing these links is the best thing I can do for now].

```{r evaluation}
# log likelihood
ll <- logLik(logit.model)

## the accurate rate of prediction is
m <- as.data.frame.matrix(table(newdata$award, pred.logit>meany2))
accrate <- (m[1,1]+m[2,2])/(m[1,1]+m[1,2]+m[2,1]+m[2,2])

## bias
mean(pred.logit) - meany2 
# A very very small number, almost 0. I have a population: meany2 is the mean of winning probabilities of the population.

@@

The log likelihood of the logit model is `r ll`. Accurate rate is `r accrate`^[I used the mean values of the outcome variable as the threshold [@bowen04]]. As for Type I error, I conducted three rounds of simulations. Each round repeated for 1000 times. The mean value of these simulations for false positive rate is `r fpr`. The standard deviation for these simulations results are `r fprsd`, which is a small number, showing that the number of simulations is satisfying. It seems that the realized size of Type I error is a little bit larger than the nominal size of Type I error.

@@

Although this interpretation of logit model looks simple and thus appealing, it avoids talking about the subtantial impact of the independent variable and the awkwardness of the concept "odds ratio". Interpretation is very important for logit models, which is unfortunately often overlooked or glossed over in many published works. However, the probability of winning and Framing Focus is not linearly related in a logit model and the marginal effect depends on the values of other covariates, so I can only interpret the substantial meaning of Framing Focus' impact under some limited conditions: With other covariates held at their mean and dummy variables at zero, moving from 25th to the 75th percentile on Framing Focus is estimated to increase the predicted probability of winning an award by `r diff.pct` percentage points.

# Appendix
As a reproducible research project, all the original data and Rmarkdown file can be accessed through my Github page <https://github.com/yingli0521/award>.
```{r appendix, results='verbatim',echo=TRUE,eval=FALSE}
<<cleaning>>
<<cleaning2>>
<<variables>>
<<summary>>
<<description>>
<<ols>>
<<ml>>
<<presentation>>
<<evaluation>>
<<biblio>>
```

>>>>

---
title: "How Does The Scope of Framing Affect Stakeholders' Evaluation of Firms?"
subtitle: "Evidence from China's State-Owned Enterprises"
author: 'Ying Li'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
geometry: margin=1.5in
fontsize: 12pt
bibliography: ref.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      tidy=T, 
                      tidy.opts=list(width.cutoff=60),
                      results='hide',
                      strip.white=TRUE,
                      fig.path='figs/fig',
                      cache=F,
                      highlight=TRUE,
                      out.width='.9\\textwidth',
                      out.extra="",
                      message=FALSE,
                      warning=FALSE,
                      error=FALSE,
                      comment=NA,
                      size='footnotesize',
                      options(digits=3,xtable.comment=FALSE))
```

@@

# Overview
Evaluation is one of the most basic social processes [@lamont12]. In the business world, garnering positive evaluations from key stakeholders such as government, media, business partners and so on is crucial for organizations to gain legitimacy, obtain resources and establish competitive advantages [@bite11]. Since social evaluation involves an information-processing mechanism that is often subjected to human cognitive and emotional factors, stakeholders' evaluation can heavily be influenced by how firms present themselves. A successful framing strategy, therefore, is essential for firms to project their identities, deliver important information, and guide social evaluation.

@@

##Variables and Measurement
```{r cleaning2,results='asis'}
# Manually check for overly influential points
library(xtable)
tabarea <- t(table(mydata$area1))
print(xtable(tabarea,label="tab:area",
             caption="Frequency of Areas. Only four observations in the overseas group is a warning signal for micronumeriosity."),
      caption.placement = "top")
print(xtable(prop.table(table(mydata$award,mydata$area1),margin=2),
             label="tab:areaaward",
             caption = "Overly Influential Points from the Overseas Area"),
      caption.placement = "top")
n_overseas <- nrow(mydata[mydata$area1=="Overseas",])
newn <- n-n_overseas
# delete four overseas firms
mydata<-mydata[!(mydata$area1=="Overseas"),]
```

@@

*Framing Focus* is the independent variable in this paper. It measures how balanced an application file is across different innovation topics. I measure this variable by calculating the standard deviation of the coverage probabilities in the three largest innovation topics in an application report. Higher Framing Focus represents that a firm is more focused on one topic instead of spanning multiple topics at the same time. The larger the value of Framing Focus, the narrower the firm frames its innovation accomplishment. For example, if the three largest coverage probabilities for firm A is (0.3, 0.3, 0.3) and for firm B is (0.4, 0.3, 0.2), then the Framing Focus for A and B are 0 and 0.1, meaning that A tries to span across multiple topics while B tries to be more focused on a smaller number of topics.

I only choose the three largest innovation topics because three different categories is already an upper limit of information for evaluators to notice and process. If all the 27 innovation topics are used, it only adds more noise because in reality almost no applicant is able to innovate in so many areas, nor would they aim to cover all the innovation topics simultaneously. For a robustness check, I also measured framing focus across four innovation topics and results are similar. In terms of the appropriateness of measurement, according to Figure 1 in @adco11, this measurement could satisfy both a top-down and bottom-up justification on four levels of conceptualization. In this paper, the background concept is firm self-presentation; the systematized concept is framing; the indicator is the focusing/spanning framing strategy of presenting innovation accomplishments in the application reports; scores for cases are standard deviations of the three most salient innovation topics' coverage.

### Control Variables
I added five control variables. *Area*. All the SOEs are divided and into four areas: North, South, East, and West. The regional economic development is very uneven in China. SOEs from different areas could have different framing strategies to present themselves and the government also evaluate SOEs from differently areas by different criteria. *Scale*. Whether an applicant firm is large- or small-size affects its ability to innovate, to frame its innovation accomplishments and thus affect its winning probability. *Ownership*. Whether an applicant firm is a Central SOE, Ordinary SOE, or other forms directly affects how much resources it can get from the central government. Ownership type is an important marker of SOE differences. *Industry*. Different industries are subjected to different evaluation criteria and tendencies to frame their innovation. I measure the industry variable by referring to the industry topic that has the largest coverage proportion. *Industry Scope*. Industry Scope is actually a second form of framing --- framing the industrial identities. Chinese SOEs are often big bureaucracies that operate across multiple industries. Some of them are so diversified because of historical reasons of assuming a specific social responsibility. Government may treat firms differently if they express their multi-industry identities in the application reports, and if a firm has a broader scope of framing in industry, it is more likely to have a broader scope of framing in innovation. I measure this variable by calculating the standard deviation of topic coverage proportions across the three largest covered industry topics.

From a design-based OLS point of view, control variables are chosen because they are corelated to both the independent variable and the dependent variable. In order to get an unbiased estimate, we need to add such kind of variables into our model. From a model-based view, however, control variables are inherently a part of the model. We include them becasue the random outcome variable is conditional on these variables. OLS can both be design-based and model-based. As will be explained later, I adopted a model-based design. Both OLS and logistic regression are modelled.

@@

## Statistical Inference
I'm interested in inferring the partial relationship between Framing Focus and probability of winning an award. I'm not using an experiment or a quasi-experiment (e.g. using matching to create an "as if" experiment) design, because my major variable of interest is continuous and dichotomizing it would sacrifice valuable information. Instead, I use a model-based design. For an OLS model, the data generating process gives probabilities of winning an award through a normal distribution. For a logit model, the data generating process gives a wining or losing binary outcome which conforms to a Bernoulli distribution. For both models, the probability of having a "success" outcome depends on a set of variables, which are ones that are listed as control variables plus the Framing Focus variable.

@@

### OLS
```{r ols}
# ols model
ols.model <- lm(award~ area + ownership + scale + industry + indvar + innvar, data = newdata)
summary(ols.model)
pred.ols <- predict(ols.model)
range <- range(pred.ols)
# bootstrapping
library(dplyr)
set.seed(1111)
bootstrap <-data.frame(t(replicate(1000,coef(lm(award~ area + ownership + scale + industry + indvar + innvar,data=sample_n(newdata,size=nrow(newdata),replace=TRUE))))))
coveint <- quantile(bootstrap[,"innvar"],c(.025,.975))
est <- mean(bootstrap[,"innvar"]) # Estimates from bootstrapping
est.sub <- sprintf("%.1f%%", est * 10) # for interpretation use
est0 <- summary(ols.model)$coef['innvar',1] # Estimates from the canned OLS model
car::vif(ols.model)
```
A binary outcome variable is not an adequate reason to exclude using OLS, especially considering that the predicted y range can provide us extra information to evaluate model specification and that we can have multiple techniques to correct for heterogeneity problems. Therefore, I first tried OLS to estimate the relationship between Framing Focus and winning probabilities.

@@

### Logistic Regression
The model specification for logistic regression is as follows:
\begin{equation}
\begin{split}
log \frac{Pr(award)}{1-Pr(award)}= \beta_{0}+\beta_{1}framing + \beta_{2}area + \beta_{3}ownership \\
+\beta_{4}scale +\beta_{5}industry + \beta_{6}industry scope + \epsilon
\end{split}
\end{equation}
Generally, for maximum likelihood method for estimation and inference, the estimates come from first-order derivative of the log likelihood function-- when the first-order derivative equals 0 the likelihood of observing the data is maximized (or minimized depending on the sign of the second derivative at this turning point), and the standard errors come from the second-order derivative. When I use logistic regression, I use maximum likelihood principles to derive estimates and standard errors. The p-values come from comparing against a t-distribution with the estimate being the mean and the stand errors being the standard deviance, what's the chance of observing such an estimate given the model is true. When sample size is large, the test statistic ($\beta/SE(\beta)$) follows an asymptotic normal distribution.

@@

# comparison of multiple link functions
pdf("pplot.pdf")
par(mfrow=c(1,2))  
plot(pred.logit,pred.probit)
plot(pred.logit,pred.clog)
dev.off()
c(logLik(logit.model),logLik(probit.model),logLik(clog.model))
```

```{r presentation, results='asis'}
est.logit <- logit.model$coefficients["innvar"]
exp.logit <- exp(0.1*est.logit)
stargazer(logit.model,omit="industry",omit.labels = "Industry Dummies", header=F,
          font.size = "small",
          title ="Maximum Likelihood Estimates for Award-Winning Odds Ratio",
          covariate.labels = c("North Area","South Area","West Area","Ordinary SOEs","Other SOEs","Small SOEs","Industry Scope","Framing Focus"),
          dep.var.labels = "Award-Winning Odds Ratio",
          label="tab:logit" #, type='text'
          )
```
Table \ref{tab:logit} describes the results of the logistic regression. The advantage of a logit model is that predictions of the dependent variable can be strictly bounded between 0 and 1. The disadvantage is that overfitting is a frequent encountered problem, but after dealing with the overly influential points, there are no apparent evidence of overfitting.

Admittedly, logit is not the only link function that can transform $X\beta$, so I also tried probit and cloglog link functions. The log likelihoods across these three link models are very close to each other and the PP-plots (Figure \ref{fig:pplot}) show that the predicted probabilities are around a 45 degree line. Given the relative advantage of interpretation of odds ratio, I only present the results of a logit model here^[I would love to evaluate the link functions using the method of [@roger06], but I have to admit that given my R skills and the limited time, manually comparing these links is the best thing I can do for now].

\begin{figure}[h]
\centering
\includegraphics[width=0.6\textwidth]{pplot.pdf}
\caption{Comparison of the Predicted Probabilities of Logit, Probit and Cloglog Links: The predicted probablities of probit and cloglog against logit are both around a 45 degree line, indicating that they are rather similar in prediction.}
\label{fig:pplot}
\end{figure}

```{r evaluation}
# separability: Given the relatively large estimates of Industry Scope and Framing Focus, is there any possbility of separability?
# plot(newdata$innvar,newdata$award)
# plot(newdata$indvar,newdata$award)
# pass the eyeball test (Fox 2008, p.388)

# multicollearity
car::vif(logit.model) # the largest one is industry: 2.65

# log likelihood
ll <- logLik(logit.model)

## the accurate rate of logit prediction is
ord <- order(pred.logit,decreasing = T)
m <- as.data.frame.matrix(table(newdata$award, ord < meany2*newn)) # result:0.672
# ord < meany2*newn. Oftentimes, 0.5 is used as a threhold, @bowen04 recommended using the mean values of the outcome variable as the threshold, but I thought may I keep the award-winning proportions consistent between the actual data and the predicted data
accrate <- (m[1,1]+m[2,2])/(m[1,1]+m[1,2]+m[2,1]+m[2,2])
pred.binary <- ifelse(ord < meany2*newn, 1, 0)
head(pred.binary)
mean(pred.binary)
var(pred.binary) > var(newdata$award)
# overdispersion? According to Fox (2008), the dispersion parameter for binominal GLMs are set to 1. So overdispersion doesn't seem to be a problem for logit models.
# Do I realy need this way to evalute a logit model? It's more like a prediction evaluation, not an inference evaluation. So, skip this.

## bias for y
mean(pred.logit) - meany2 
# A very very small number, almost 0. I have a population: meany2 is the mean of winning probabilities of the population.

@@

The log likelihood of the logit model is `r ll`. As for Type I error, I conducted three rounds of simulations. Each round repeated for 1000 times. The mean value of these simulations for false positive rate is `r fpr`. The standard deviation for these simulations results are `r fprsd`, which is a small number, showing that the number of simulations is satisfying. It seems that the realized size of Type I error is a little bit larger than the nominal size of Type I error.

@@

Although this interpretation of logit model looks simple and thus appealing, it avoids talking about the substantial impact of the independent variable and the awkwardness of the concept "odds ratio". Interpretation is very important for logit models, which is unfortunately often overlooked or glossed over in many published works. However, the probability of winning and Framing Focus is not linearly related in a logit model and the marginal effect depends on the values of other covariates, so I can only interpret the substantial meaning of Framing Focus' impact under some limited conditions: With other covariates held at their mean and dummy variables at zero, moving from 25th to the 75th percentile on Framing Focus is estimated to increase the predicted probability of winning an award by `r diff.pct` percentage points.

# Appendix
As a reproducible research project, all the original data and Rmarkdown file can be accessed through my Github page <https://github.com/yingli0521/award>.
```{r appendix, results='verbatim',echo=TRUE,eval=FALSE}
<<setup>>
<<cleaning>>
<<cleaning2>>
<<variables>>
<<summary>>
<<description>>
<<ols>>
<<ml>>
<<presentation>>
<<evaluation>>
<<biblio>>
```

### 2018-05-15 template.Rmd
updata
up

---
title: 'Title'
author: '[Ying Li](https://business.illinois.edu/profile/ying-li/)'
date: '`r format(Sys.Date())`'
fontsize: 12pt
geometry: margin=1in
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    fig_height: 4
    fig_width: 4
---

```{r globalsettings, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  tidy=TRUE,
  echo=FALSE,
  message=FALSE,
  results='asis',
  strip.white=TRUE,
  fig.path='Figures/',
  cache=FALSE,
  highlight=TRUE,
  width.cutoff=80,
  size='footnotesize',
  out.width='.9\\textwidth',
  fig.retina=FALSE,
  comment=NA,
  out.extra="")

if(!file.exists('Figures/')) dir.create('Figures/')
```

```{r eval=FALSE}
# Frequentely used:
- Insert a figure
\begin{figure}
\includegraphics{bayesplot.png}
\caption{Estimates and Credible Intervals of A Bayesian Logit Model}
\label{fig:bayesplot}
\end{figure}
Figure \ref{fig:bayesplot}
```

>>>>

---
title: 'Title'
author: '[Ying Li](https://business.illinois.edu/profile/ying-li/)'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 12pt
geometry: margin=1in
header-includes: \usepackage{setspace}\doublespacing
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    fig_height: 4
    fig_width: 4
---

```{r globalsettings, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  tidy=TRUE,
  tidy.opts=list(width.cutoff=80),
  echo=FALSE,
  message=FALSE,
  warning=FALSE,
  error=FALSE,
  collapse = TRUE,
  highlight=TRUE, # Increase the readability of source code syntax
  results='asis',
  strip.white=TRUE, #To skip white lines
  fig.path='Figures/',
  cache=TRUE,
  cache.path='cache/',
  award_time=file.info('award.csv')$mtime, # data will be re-read if award.csv becomes newer
  width.cutoff=80,
  size='footnotesize', # Other options include small, large, Large
  out.width='.9\\textwidth',
  fig.retina=FALSE,
  comment=NA,
  out.extra="")
if(!file.exists('Figures/')) dir.create('Figures/')
options(scipen = 1, digits = 2)
```

```{r eval=FALSE}
# Frequentely used:
- Insert a figure
\begin{figure}
\includegraphics{bayesplot.png}
\caption{Estimates and Credible Intervals of A Bayesian Logit Model}
\label{fig:bayesplot}
\end{figure}
Figure \ref{fig:bayesplot}

# Appendix 
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
If you want to remove the first chunk, you can write knitr::all_labels()[-1].
Of course, this requires you to give a label to each chunk.
```

# Appendix^[I ]
```{r appendix, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
